Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-17 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Fix references in Madrzykowski thesis

Cone calorimeter (ASTM~1354) experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$.

@@

The cone calorimeter is one of the most commonly used bench-scale rate of heat release apparatus that uses the oxygen consumption method. It was developed at NIST in the 1980s~\cite{babrauskas:1984}. The cone calorimeter has been adopted as ASTM E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter~\cite{ASTM E1354}. The cone calorimeter consists of a heater, spark ignitor, sample holder, and load cell located underneath an exhaust hood. Typically, the sample is located in the open with free access of air to the combustion zone. The heater consists of a 5~kW electrical heating element inside an insulated stainless-steel conical shell. Samples can be tested in either a horizontal or vertical orientation. When tests are performed in the horizontal configuration, the specimen is positioned approximately 25~mm beneath the bottom plate of the cone heater. Flames and products of combustion pass through a circular opening at the top of the heater. The heater can expose samples to a maximum irradiance of approximately 100~kW/m$^2$. Figure  is a schematic of the cone calorimeter.

>>>>

Cone calorimeter~\cite{ASTM_E1354} experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$.

@@

The cone calorimeter is one of the most commonly used bench-scale rate of heat release apparatus that uses the oxygen consumption method. It was developed at NIST in the 1980s~\cite{babrauskas:1984}. The cone calorimeter has been adopted as ASTM~E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter~\cite{ASTM_E1354}. The cone calorimeter consists of a heater, spark ignitor, sample holder, and load cell located underneath an exhaust hood. Typically, the sample is located in the open with free access of air to the combustion zone. The heater consists of a 5~kW electrical heating element inside an insulated stainless-steel conical shell. Samples can be tested in either a horizontal or vertical orientation. When tests are performed in the horizontal configuration, the specimen is positioned approximately 25~mm beneath the bottom plate of the cone heater. Flames and products of combustion pass through a circular opening at the top of the heater. The heater can expose samples to a maximum irradiance of approximately 100~kW/m$^2$. Figure  is a schematic of the cone calorimeter.
